Efficient forwards-time simulation with ancestral recombination graphs

### 2017-10-23 forwards_paper.tex
changed ARG references

\begin{figure}
    \begin{center}
        \includegraphics[width=\textwidth]{example_tree_sequence}
    \end{center}
    \caption{
        An example tree sequence with three samples over a chromosome of length 10. In the
        left-most panel we show the tree sequence pictorially in two different ways:
        in the top are the tree topologies and the bottom shows the spatial extent of the
        edges that define these topologies. The right-hand panels show the specific encoding
        of this tree sequence in the four tables (nodes, edges, sites and mutations) defined
        by \msprime.
        \jk{The figure needs to be rescaled a bit to give more space to the trees. We could also use a
        time scale next to the trees.}
        \label{fig:example_tree_sequence}
    }
\end{figure}

@@

Given the topology defined by the nodes and edges, \emph{sites} and \emph{mutations}
encode the sequence information for each sample in an efficient way. Each site
is associated with a position on the genome and an ancestral state. For example,
in Figure~\ref{fig:example_tree_sequence} we have two sites, one at position
2 and ancestral state `A' and the other at position 7 with ancestral state `G'. If
no mutations occur, all samples inherit the ancestral state at a given site.
A mutation occurs over a specific node at a given site, and results in a specific
derived state. Thus, all samples below the mutation node in the tree will inherit
this state (unless further mutations are encountered). Three mutations are shown
in Figure~\ref{fig:example_tree_sequence}, illustrated by red hexagons. The first
mutation occurs at site zero (which is in the left-hand tree), which is a simple
mutation resulting in node $2$ inheriting the state 'T'. The second side (in the
right hand tree) has two mutations: one occuring over node $3$ changing the state to
`C' and a back mutation over node $1$ changing the state to `G'.
\jk{Not sure if I'm labouring the point here: this should be reasonably obvious.
Perhaps if we added the state changes to the trees, and the states of the leaves
below the samples, we could get rid of all the example discussion here?}

@@

@@

\subsection*{Data structures:}
\jk{Moved from above.}

>>>>

\begin{figure}
    \begin{center}
        \includegraphics[width=0.6\textwidth]{example_tree_sequence}
    \end{center}
    \caption{
        An example tree sequence with three samples over a chromosome of length 10. In the
        left-most panel we show the tree sequence pictorially in two different ways:
        in the top are the tree topologies and the bottom shows the spatial extent of the
        edges that define these topologies. The right-hand panels show the specific encoding
        of this tree sequence in the four tables (nodes, edges, sites and mutations) defined
        by \msprime.
        \label{fig:example_tree_sequence}
    }
\end{figure}

@@

\jk{Continue along these lines with sites and mutations after updating the figure}

@@

\subsection*{Data structures:}

@@
